### 2008-12-11 doc/client/client_technical.tex
Replaced sentences containing the word propriety. Probably the intention was that they should say propietary, but since the things being described weren't proprietary other words were used instead.
Starting broker latex documentation

Job submission starts with the resource discovery and target
preparation as outlined in the Section~\ref{sec:TargetDiscovery}. Not
until a list of possible targets (which allows the user) is available
is the job description read in order to enable bulk job submission of
widely different jobs without having to reperform the resource
discovery. In addition to the classes mentioned above the job
submission makes use of the {\Broker}, {\JobDescription} and
{\Submitter} classes. At the time of writing the {\Broker} is not
implemented, but it's functionality and interface is well known, and
thus we will include it in the overview given here. The {\Submitter}
is base class for further grid middleware specific specialization
(plugin) similarly to the {\TargetRetriever}.

@@

The {\Broker} is not yet implemented and thus not described here.

@@

The ARC 0.x local information system uses the {\GT}~\cite{globus} GRIS
with a propriety ARC schema. The information index server used is the
{\GT} GIIS. Both these servers are using the LDAP~\cite{ldap}
protocol. The specialization of the {\TargetRetriever} class for ARC0
is implemented using the ARC LDAP Data Management Component (DMC) (see
\cite{hed} for technical details).

@@

The CREAM interface is a propriety SOAP based interface. The CREAM
specializations of the {\Submitter} and {\JobController} classes
therefore use an MCC chain ending with the SOAP client MCC the same 
way the ARC1 plugin does.

>>>>

Job submission starts with the resource discovery and target
preparation as outlined in the Section~\ref{sec:TargetDiscovery}. Not
until a list of possible targets (which allows the user) is available
is the job description read in order to enable bulk job submission of
widely different jobs without having to reperform the resource
discovery. In addition to the classes mentioned above the job
submission makes use of the {\Broker}, {\JobDescription} and
{\Submitter} classes.  The {\Submitter} is base class for further grid
middleware specific specialization (plugin) similarly to the {\TargetRetriever}.

@@

There are two usable broker type at the current state: \textbf{FastQueueBroker} and \textbf{RandomBroker}. These classes are inheritance of the "super \textbf{Broker}" class. This parent class has a prefiltering part and its task is to create a mapping between the \textbf{JobDescription} and the \textbf{ExecutionTarget}. The mapping is working but it will be change at the near future because the \textbf{JobDescription} class will be  recreate with \textbf{GIN Profile JSDL}. The mapping result is the \textbf{PossibleTargets} vector which content the "good" \textbf{ExecutionTargets}. The descendant broker classes task is to sort the \textbf{PossibleTargets} vector with its name type, for example: \textbf{RandomBroker} sort type is \textbf{Random}. The broker separated into a module therefore it is loadable.

@@

The ARC 0.x local information system uses the {\GT}~\cite{globus} GRIS
with a purpose made ARC schema. The information index server used is the
{\GT} GIIS. Both these servers are using the LDAP~\cite{ldap}
protocol. The specialization of the {\TargetRetriever} class for ARC0
is implemented using the ARC LDAP Data Management Component (DMC) (see
\cite{hed} for technical details).

@@

CREAM has its own SOAP based interface. The CREAM
specializations of the {\Submitter} and {\JobController} classes
therefore use an MCC chain ending with the SOAP client MCC the same 
way the ARC1 plugin does.
